Exploring Crete's Macroecology based on its soil Microbial Interactome

### 2023-12-25 manuscript.tex
add refs of Vogiatzakis

\title[Crete's soil microbiome]{Defining Crete's Macroecology based on its soil Microbial Interactome}

@@

Islands are nature's labs \citep{Whittaker2017} and in soil microbes \citep{Li2020} and fungi \citep{Delavaux2021}
Ultimately islands can set the ground to represent ecosystems with data and complex interactions \citep{Davies2016}.

Genome Standards Consortium \citep{Field2011}, FAIR data \citep{Wilkinson2016}, unrestricted \citep{Amann2019},
rich metadata and platforms of hosting open data like European Soil Data Centre \citep{Panagos2022}

>>>>

\title[Crete's soil microbiome]{Exploring Crete's Macroecology based on its soil Microbial Interactome}

@@

Islands are nature's labs \citep{Whittaker2017} and in soil microbes \citep{Li2020} and fungi \citep{Delavaux2021}
Ultimately islands can set the ground to represent ecosystems with data and complex interactions \citep{Davies2016}.
\citep{Vogiatzakis2008_crete}
\citep{Vogiatzakis2016}

\citep{Sfenthourakis2017}
\citep{Vogiatzakis2008_med}
Genome Standards Consortium \citep{Field2011}, FAIR data \citep{Wilkinson2016}, unrestricted \citep{Amann2019},
rich metadata and platforms of hosting open data like European Soil Data Centre \citep{Panagos2022}
